Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/eval.tex
shrink more

Push-Pull BFS in Finch:
\begin{minted}{julia}
V = Tensor(Dense(Element(false)))
P = Tensor(Dense(Element(0)))
F = Tensor(SparseByteMap(Pattern()))
_F = Tensor(SparseByteMap(Pattern()))
A = Tensor(Dense(SparseList(Pattern())))
AT = Tensor(Dense(SparseList(Pattern())))

function finch_bfs_push_kernel(_F, F, A, V, P)
    @finch begin
        _F .= false
        for j=_, k=_
            if F[j] && A[k, j] && !(V[k])
                _F[k] |= true
                P[k] <<choose(0)>>= j #Only set the parent for this vertex
            end
        end
        return _F
    end
end

function finch_bfs_pull_kernel(_F, F, AT, V, P)
    p = ShortCircuitScalar{0}()
    @finch begin
        _F .= false
        for k=_
            if !V[k]
                p .= 0
                for j=_
                    if F[follow(j)] && AT[j, k]
                        p[] <<choose(0)>>= j #Only set the parent for this vertex
                    end
                end
                if p[] != 0
                    _F[k] |= true
                    P[k] = p[]
                end
            end
        end
        return _F
    end
end
\end{minted}

>>>>

\begin{figure}
    \begin{minipage}{0.5\linewidth}
    \begin{minted}{julia}
    V = Tensor(Dense(Element(false)))
    P = Tensor(Dense(Element(0)))
    F = Tensor(SparseByteMap(Pattern()))
    _F = Tensor(SparseByteMap(Pattern()))
    A = Tensor(Dense(SparseList(Pattern())))
    AT = Tensor(Dense(SparseList(Pattern())))

    function finch_bfs_push_kernel(_F, F, A, V, P)
        @finch begin
            _F .= false
            for j=_, k=_
                if F[j] && A[k, j] && !(V[k])
                    _F[k] |= true
                    P[k] <<choose(0)>>= j
                end
            end
            return _F
        end
    end

    \end{minted}
\end{minipage}%
\begin{minipage}{0.5\linewidth}
    \begin{minted}{julia}
    function finch_bfs_pull_kernel(_F, F, AT, V, P)
        p = ShortCircuitScalar{0}()
        @finch begin
            _F .= false
            for k=_
                if !V[k]
                    p .= 0
                    for j=_
                        if F[follow(j)] && AT[j, k]
                            p[] <<choose(0)>>= j
                        end
                    end
                    if p[] != 0
                        _F[k] |= true
                        P[k] = p[]
                    end
                end
            end
            return _F
        end
    end
    \end{minted}
\end{minipage}
\end{figure}
